Can Auxiliary Indicators Improve COVID-19 Forecasting and Hotspot Prediction?

### 2021-11-09 forecast/paper/supplement-medrxiv.tex

\caption{Relative forecast performance using vintage data and summarizing with the more robust geometric mean.}\label{fig:fcast-adjusted}
\end{figure}

@@

@@

\caption{Classification and loglikelihood separated into periods of upswing, downswing, and flat cases. Like the analysis of the forecasting task in the main paper (see Figure 7), performance is better during down and flat periods.}\label{fig:hotspots-upswing-downswing}
\end{figure}

@@

\caption{Histograms of the Spearman correlation between the ratio of AR to AR WIS with the percent change in smoothed case rates relative to 7 days earlier.}\label{fig:cor-wis-ratio}
\end{figure}

@@

\caption{Correlation of the difference in WIS with the difference in median predictions for the AR model relative to the indicator-assisted forecaster. In down periods, improvements in forecast risk are highlycorrelated with lower median predictions. The opposite is true in up periods. This suggests, as one might expect that improved performance of the indicator-assisted model is attributable to being closer to the truth then the AR model. This conclusion is stronger in down periods then in up periods.}\label{fig:upswing-corr-table}
\end{figure}

@@

\caption{Illustration of the cross-correlation function between DV-CLI and cases. The left panel shows the standardized signals over the period from August 1 to September 28 (as of May 15, 2021). The right panel shows $\CCF_{\ell}(a)$ for different values of $a$ as vertical blue bars. The orange dashed lines indicate the 95\% significance threshold. By our leadingness/laggingness metric, DV-CLI is leading (but notlagging) cases over this period.}\label{fig:ccf-dv-finalized}
\end{figure}

@@

{\centering \includegraphics[width=\textwidth]{fig/fcast-alldates-1}

\caption{Forecast performance over all periods. Performance largely improves for all forecasters with the inclusion of data in 2021.}\label{fig:fcast-alldates}
\end{figure}

@@

{\centering \includegraphics[width=\textwidth]{fig/fcast-alldates-adjusted-1}

@@

\caption{Forcast performance over all periods aggregaged with the geometric mean. Again, the inclusion of data in 2021 leads to improved performance.}\label{fig:fcast-alldates-adjusted}
\end{figure}

@@

{\centering \includegraphics[width=\textwidth]{fig/hot-alldates-1}

@@

\caption{Area under the curve for hotspot predictions including data in 2021. Performance degrades relative to the period in 2020. However, there are far fewer hotspots during this period as case rates declined in much of the country.}\label{fig:hot-alldates}
\end{figure}

%\bibliography{../../common/covidcast.bib,pnas-materials/pnas-sample.bib}

>>>>

\caption{Forecast performance (using vintage data), summarized by geometric mean.}\label{fig:fcast-adjusted}
\end{figure}

@@

{\centering \includegraphics[width=\textwidth]{fig/compare-states-to-hub}

\caption{Forecast performance for AR and indicator models, each retrained at the state level, compared to models submitted to the COVID-19 Forecast Hub over the same period. The thin grey lines are individual models from the Hub; the light blue line is the Hub ensemble model. To align prediction dates as best as possible, we look at the AR and indicator model forecasts for 5, 12, 19, and 26 days ahead; this roughly corresponds to 1, 2, 3, and 4 weeks ahead, respectively, since in the Hub, models typically submit forecasts on a Tuesday for the epiweeks aligned to end on each of the following 4 Saturdays.}\label{fig:compare-to-hub}
\end{figure}

{\centering \includegraphics[width=\textwidth]{fig/sign-test-1}

\caption{P-values from a one-sided sign test for improved forecast performance of the indicator-assisted models. Each p-value corresponds to a forecast date. The alternative hypothesis is that the AR model is better (median difference between the relative WIS of the AR model and an indicator model is negative).}\label{fig:sign-test}
\end{figure}

\begin{table}

\caption{\label{tab:dm-test}P-values from a one-sided Diebold-Mariano test for improvemed forecast performance when adding the indicators. The alternative hypothesis is that the AR model is better.}
\centering
\begin{tabular}[t]{lrrrrr}
\toprule
metric & CHNG-CLI & CHNG-COVID & CTIS-CLIIC & DV-CLI & Google-AA\\
\midrule
Geometric mean & 0.072 & 0.036 & 0.005 & 0.032 & 0.026\\
Mean & 0.177 & 0.132 & 0.006 & 0.092 & 0.103\\
\bottomrule
\end{tabular}
\end{table}

@@

\caption{Percentage change in classification error and log likelihood, relative that of the AR model, separated into up, down, and flat periods. Like the analogous forecasting analysis, the indicator models generally do better during down and flat periods.}\label{fig:hotspots-upswing-downswing}
\end{figure}

@@

\caption{Histograms of the Spearman correlation between the ratio of forecaster WIS to AR WIS with the \% change in case rates, relative to case rates 7 days earlier.}\label{fig:cor-wis-ratio}
\end{figure}

@@

\caption{Correlation of the difference in WIS with the difference in median predictions (each difference being between the AR model and an indicator model), separated into up, down, and flat periods. In down periods, improvements in forecast error are highly correlated with lower median predictions. The opposite is true in up periods, but the conclusion here appears to be weaker.}\label{fig:upswing-corr-table}
\end{figure}

{\centering \includegraphics[width=\textwidth]{fig/upswing-summary-remake-1}

\caption{Percentage change in average WIS of the forecaster (AR or indicator assisted), relative to the baseline. All models perform poorly during down periods, but the indicators help. During flat periods, the indicators improve slightly over the AR. During up periods, all forecasters do much better than the baseline, but only some do as well as AR.}\label{fig:upswing-summary-remake}
\end{figure}

@@

\caption{Illustration of the cross-correlation function between DV-CLI and cases. The left panel shows the standardized signals over the period from August 1 to September 28 (as of May 15, 2021). The right panel shows $\CCF_{\ell}(a)$ for different values of $a$ as vertical blue bars. The orange dashed line indicates the 95\% significance threshold. By our leadingness/laggingness metric, DV-CLI is leading (but not lagging) cases over this period.}\label{fig:ccf-dv-finalized}
\end{figure}

@@

@@

{\centering \includegraphics[width=\textwidth]{fig/cumulative-mean-1}

@@

\caption{Cumulative sum of WIS for each forecaster divided by the cumulative sum of WIS for the baseline model. The shaded background shows national case incidence for the 14-day ahead target. Hash marks along the x-axis denote weeks.}\label{fig:cumulative-mean}
\end{figure}

@@

{\centering \includegraphics[width=\textwidth]{fig/errs-in-space-1}

@@

\caption{Percentage improvement in WIS, relative to the AR forecaster, by HRR (negative numbers indicate improved performance, positives indicate worsening).}\label{fig:errs-in-space}
\end{figure}
